---
title: "Task4_Chiara_Laudani"
author: "Chiara Laudani"
date: "11/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse) #General-purpose data wrangling
library(lubridate) #Eases DateTime manipulation
library(zoo) #for as.Date
library(dplyr) #For grouping and counting the rows per month
library(ggplot2)
library(readr)
library(knitr)

data <- read.csv("storedata.csv")
```

The first task for this week is to calculate the total Sales by month for the last 3 months of 2017, for Region 1 and Region 9, in the Customer_Segment "Corporate" and "Consumer".

```{r}
q1 <- data %>%
    mutate(Order_Date = as.Date(data$Order_Date, format = "%Y-%m-%d")) %>%
  filter(Order_Date >= as.Date('2017-10-01') & Order_Date <= as.Date('2017-12-31')) %>%
  filter(Region == "Region 1" | Region == "Region 9") %>%
  filter(Customer_Segment == "Corporate" | Customer_Segment == "Consumer") %>% 
  select(Order_Date, Sales, Region) %>%
  group_by(Region, as.yearmon(Order_Date)) %>%
  summarise(Total_Sales = sum(Sales)) 
colnames(q1)[2] <- "Month_Year"
kable(q1, caption = "Table 1")
```

The second task asks us to make a plot of the monthly total Sales in Region 1 and Region 13 in 2015, 2016 and 2017.

```{r}
q2 <- data %>%
  mutate(Order_Date = as.Date(data$Order_Date, format = "%Y-%m-%d")) %>%
  filter(Order_Date >= as.Date('2015-01-01') & Order_Date <= as.Date('2017-12-31')) %>%
  filter(Region == "Region 1" | Region == "Region 13") %>%
  select(Order_Date, Sales, Region) %>%
  group_by(Region, as.yearmon(Order_Date)) %>%
  summarise(Total_Sales = sum(Sales)) 

colnames(q2)[2] <- "Month_Year"

# Figure 1
ggplot(q2, aes(x=Month_Year, y=Total_Sales, color=Region, fill=Region)) +
  scale_x_continuous() +
  geom_line() + 
  geom_point(alpha=0.4) +
  xlab("Date") + 
  ylab("Total sales per month") + 
  ggtitle("Figure 1 - Monthly sales")
```

Task 3 asks to identify the months where the total Sales in Region 13 is greater than the total Sales in Region 1. 
```{r}
q3 <- q2 %>% 
  spread(Region, Total_Sales) %>% 
  filter(`Region 13` > `Region 1`) #use `` to make the text not a string, but a evaluatable object
kable(q3, caption = "Table 2")
```

Task 4 is to find the average Profit per Customer_Segment and Product_Category in 2017, for all regions except Region 3, 5 and 8.
```{r}
q4 <- data %>%
  mutate(Order_Date = as.Date(data$Order_Date, format = "%Y-%m-%d")) %>%
  filter(Order_Date >= as.Date('2017-01-01') & Order_Date <= as.Date('2017-12-31')) %>%
  filter(Region != "Region 3" & Region != "Region 5" & Region != "Region 8") %>% 
  group_by(Customer_Segment, Product_Category) %>% 
  summarise(average_profit = mean(Profit)) %>% 
  arrange(desc(average_profit))

kable(q4, caption = "Table 3")
```

The segment which produced the highest average profit was: `r kable(q4[1,])`

The final task, Taks 5, asks to estimate a SARIMA model on the aggregated monthly Order_Quantity in the Customer_Segment; Small Business and Product_Category; Office Supplies.